Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-08-26 2015-turklang-kazdep/paper.tex
some table 4 updates because of recent change
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61591 72bbbca6-d526-0410-a7d9-f06f51895060
a little more detail
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61592 72bbbca6-d526-0410-a7d9-f06f51895060

Table~\ref{tab:casefunc} details the various tags (i.e., syntactic functions) associated with the traditionally defined morphological cases of Kazakh.  It should be noted that there are several known uses which are currently unattested (partitive use of \gmk{abl} as \udtag{dobj}, embedded \udtag{subj} marked as \gmk{acc}) or rare (\gmk{dat} as \udtag{iobj}) in the corpus.

\begin{table}[htbp]
	\centering
	\caption{The functions associated with each case in Kazakh as currently found in the corpus.}
	\label{tab:casefunc}
	\begin{tabular}{lrrrrrrrr}
		\toprule
			 & \udtag{iobj} & \udtag{cmpnd} & \udtag{nmod} & \udtag{nmod:poss} & \udtag{dobj} & \udtag{root} & \udtag{subj} & \udtag{voc} \\
		\midrule
			\gmk{nom} & — & 1 & 199 & 158 & 72 & 26 & 279 & 1 \\
			\gmk{acc} & — & — & 1 & — & 101 & — & — & — \\
			\gmk{gen} & — & — & 120 & 120 & — & — & 12 & — \\
			\gmk{dat} & 1 & — & 113 & — & 13 & — & — & — \\
			\gmk{loc} & — & — & 112 & 1 & — & 6 & — & — \\
			\gmk{abl} & — & — & 64 & — & — & — & — & — \\
			\gmk{ins} & — & — & 33 & — & — & — & — & — \\
		\bottomrule
	\end{tabular}
\end{table}
\vspace{-0.75em}

>>>>

Table~\ref{tab:casefunc} briefly details the various tags (i.e., syntactic functions) associated with the traditionally defined morphological cases of Kazakh as found in the corpus.  Some mappings may be surprising, but will not be discussed in detail in this paper.  It should also be noted that there are several known uses which are currently unattested (partitive use of \gmk{abl} as \udtag{dobj}, embedded \udtag{subj} marked as \gmk{acc}) or rare (\gmk{dat} as \udtag{iobj}) in the corpus.

\begin{table}[htbp]
	\centering
	\caption{The functions associated with each case in Kazakh as currently found in the corpus.}
	\label{tab:casefunc}
	\begin{tabular}{lrrrrrrrr}
		\toprule
			 & \udtag{iobj} & \udtag{cmpnd} & \udtag{nmod} & \udtag{nmod:poss} & \udtag{dobj} & \udtag{root} & \udtag{subj} & \udtag{voc} \\
		\midrule
			\gmk{nom} & — & 1 & 199 & 157 & 72 & 26 & 279 & 1 \\
			\gmk{acc} & — & — & 1 & — & 101 & — & — & — \\
			\gmk{gen} & — & — & 120 & 120 & — & — & 12 & — \\
			\gmk{dat} & 1 & — & 113 & — & 13 & — & — & — \\
			\gmk{loc} & — & — & 113 & — & — & 6 & — & — \\
			\gmk{abl} & — & — & 64 & — & — & — & — & — \\
			\gmk{ins} & — & — & 33 & — & — & — & — & — \\
		\bottomrule
	\end{tabular}
\end{table}
\vspace{-0.75em}
